A Review on Interactive Adaptive Processes Which Underline Short-Term Motor Learning

### 2022-06-26 Report/PaperReport.tex
long references are modified

% If your first paragraph (i.e. with the \dropcap) contains a list environment (quote, quotation, theorem, definition, enumerate, itemize...), the line after the list may have some extra indentation. If this is the case, add \parshape=0 to the end of the list environment.
\section*{Introduction}
\dropcap{R}elearning a previously unlearned stimulus-response relationship is faster than the initial learning in case of savings in the system \cite{main_paper}. Compensating the disturbance from the external environment or the motor system itself is called motor adaptation. Recent studies show savings in motor adaptation  \cite{Kojima}. Also, better performance is reported by having no feedback trials between extinction and re-adaptation trials \cite{Kojima}. 
Until now, three models of trial-to-trial adaptation is proposed: Single state, Gain specific, and Multi rate. The single state model predicts the motor responses to disturbances and successfully assesses the pattern of generalization [\cite{Scheidt}, \cite{Baddeley}, \cite{Thoroughman}, and \cite{Donchin}]; But the problem is that this model is single time constant adaptation and this leads to failure in other experiments like anterograde interference, rapid de-adaptation, and rapid downscaling. In the anterograde interference paradigm we have an initial learning block and then a de-adaptation block in which we expect to have lower performance and a slower time constant for the de-adaptation block [\cite{Bizzi}, \cite{shadmehr_jn}, \cite{Wolpert}] . A two-state model is suggested by Kojima et al. which can successfully model saving and washout of saving but fails for recovery of the initially adapted state in no feedback error block and also fails for described anterograde interference \cite{Kojima}.
In this report, we showed that the multi time constant model proposed by Smith et al. can correctly model the motor response under different experiments and paradigms \cite{main_paper}. Herzfeld et al. also presented a model in which they showed that the brain decides how much to learn from a current error based on the history of previous errors \cite{mem_error}. This is also implemented and tested under different disturbances.\\

>>>>

% If your first paragraph (i.e. with the \dropcap) contains a list environment (quote, quotation, theorem, definition, enumerate, itemize...), the line after the list may have some extra indentation. If this is the case, add \parshape=0 to the end of the list environment.
\section*{Introduction}
\dropcap{R}elearning a previously unlearned stimulus-response relationship is faster than the initial learning in case of savings in the system \cite{main_paper}. Compensating the disturbance from the external environment or the motor system itself is called motor adaptation. Recent studies show savings in motor adaptation \cite{Kojima}. Also, better performance is reported by having no feedback trials between extinction and re-adaptation trials \cite{Kojima}. 
Until now, three models of trial-to-trial adaptation is proposed: Single state, Gain specific, and multi-rate. The single state model predicts the motor responses to disturbances and successfully assesses the pattern of generalization [\cite{Scheidt} - \cite{Donchin}]; But the problem is that this model is single-time constant adaptation and this leads to failure in other experiments like anterograde interference, rapid de-adaptation, and rapid downscaling. In the anterograde interference paradigm we have an initial learning block and then a de-adaptation block in which we expect to have lower performance and a slower time constant for the de-adaptation block [\cite{Bizzi} - \cite{Wolpert}]. A two-state model is suggested by Kojima et al. which can successfully model saving and washout of saving but fails for recovery of the initially adopted state in no feedback error block and also fails for described anterograde interference \cite{Kojima}.
In this report, we showed that the multi-time constant model proposed by Smith et al. can correctly model the motor response under different experiments and paradigms \cite{main_paper}. Herzfeld et al. also presented a model in which they showed that the brain decides how much to learn from a current error based on the history of previous errors \cite{mem_error}. This is also implemented and tested under different disturbances.\\
